=enter title here=

### 2024-11-18 ms/ms.tex
intro

>>>>

The 2020 Southwest U.S. drought was the driest summer of the instrumented record and part of a 20-year megadrought with severe consequences for water resources.

Coupled ESMs have not captured humidity trends in semi-arid ecosystems \cite{simpson2024}.

Though ESMs show a slight increase in spring precipitation in the region, there does not seem to be an attributable influence of climate change on NAM precipitation. Previous work indicates that the 2020 SWUS drought was not exacerbated by climate change, but was rather a result of  internal atmospheric variability \cite{seager2022}.
